Turned on!": Momentum in Round-Based First Person Shooter Esports

### 2022-07-22 presentation.qmd
start trying logos

```{r}
#| label: setup-eval
library(tidyverse)
library(extrafont)
library(ggtext)
library(ggsci)
library(ggnewscale)
blackish_background <- '#191919' ## to match slide background
gray_points <- '#4d4d4d'
gray_text <- '#999999'

font <- 'Titillium Web'
extrafont::loadfonts(quiet = TRUE)
theme_set(theme_minimal())
theme_update(
  text = element_text(family = font),
  title = element_text(size = 14, color = 'white'),
  plot.title = element_text(face = 'bold', size = 20, color = 'white'),
  plot.title.position = 'plot',
  plot.subtitle = element_text(size = 14, color = '#f1f1f1'),
  axis.text = element_text(color = 'white', size = 14),
  axis.title = element_text(size = 14, color = 'white', face = 'bold', hjust = 0.99),
  axis.line = element_blank(),
  panel.grid.major = element_line(color = gray_points),
  panel.grid.minor = element_line(color = gray_points),
  panel.grid.minor.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  strip.text = element_text(color = 'white', size = 16, face = 'bold'),
  plot.margin = margin(10, 10, 10, 10),
  plot.background = element_rect(fill = blackish_background, color = blackish_background),
  plot.caption = element_text(size = 12, color = 'white', hjust = 1),
  plot.caption.position = 'plot',
  plot.tag = ggtext::element_markdown(size = 12, color = 'white', hjust = 0),
  plot.tag.position = c(0.01, 0.01),
  panel.background = element_rect(fill = blackish_background, color = blackish_background)
)
update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
update_geom_defaults('point', list(color = 'white'))
update_geom_defaults('segment', list(color = 'white'))
```

@@

## What are your chances of winning a round, given the series state in [COD SnD]{.cod}?

@@

.dpi <- 300
save_for_slide <- function(
    p, 
    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
    width = 7.5, 
    height = width / 1.5,
    units = 'px',
    dpi = .dpi,
    ...
) {
  ggsave(
    plot = p,
    filename = filename,
    width = width * dpi,
    height = height * dpi,
    units = units,
    dpi = dpi,
    ...
  )
}

@@

p_cod_o_round_win_prop <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop,
    .f = o_round_win_text_layer,
    .threshold = 0.52,
    .labeller = cod_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_cod_o_round_win_prop
save_for_slide(p_cod_o_round_win_prop)
```

@@

cod_max_diff_win_round_prop <- max(abs(cod_o_win_prop$diff_win_round_prop))
p_cod_o_round_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'diff_win_round_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_round_win_over_expected_text_layer,
    .threshold = -0.1,
    .labeller = cod_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('purple'),
    high = extract_ggsci_mid_color('green'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_round_prop, 
      +cod_max_diff_win_round_prop
    )
  ) +
  labs(
    title = 'Offensive Round Win % Over Expected'
  )
p_cod_o_round_win_prop_over_expected
save_for_slide(p_cod_o_round_win_prop_over_expected)
```

@@

## What are your chances of winning a round, given the series state in [Valorant]{.valorant}?

@@

p_val_o_round_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  geom_path(
    data = val_pre_swap_round_segments,
    color = 'white',
    size = 1.5,
    aes(
      x = pre_cumu_w, 
      y = pre_cumu_l
    )
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_round_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_val_o_round_win_prop
save_for_slide(p_val_o_round_win_prop)
```

@@

## What are your chances of winning the series, given the series state in [COD SnD]{.cod}?

@@

p_cod_o_series_win_prop <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'win_series_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_series_win_text_layer,
    .threshold = 0.8,
    .labeller = cod_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('orange') +
  labs(
    title = 'Offensive Series Win %'
  )
p_cod_o_series_win_prop
save_for_slide(p_cod_o_series_win_prop)
```

@@

cod_max_diff_win_series_prop <- max(abs(cod_o_win_prop$diff_win_series_prop))
p_cod_o_series_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.08,
    .labeller = cod_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_series_prop, 
      +cod_max_diff_win_series_prop
    )
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_cod_o_series_win_prop_over_expected
save_for_slide(p_cod_o_series_win_prop_over_expected)
```

@@

## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?

```{r}
#| label: p_val_o_series_win_prop
p_val_o_series_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_series_prop') +
  geom_path(
    data = val_pre_swap_round_segments,
    color = 'white',
    size = 1.5,
    aes(
      x = pre_cumu_w, 
      y = pre_cumu_l
    )
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('orange') +
  labs(
    title = 'Offensive Series Win %'
  )
p_val_o_series_win_prop
save_for_slide(p_val_o_series_win_prop)
```

@@

## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?

@@

val_max_diff_win_series_prop <- max(abs(val_o_win_prop$diff_win_series_prop))
p_val_o_series_win_prop_over_expected <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.2,
    .labeller = val_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    limits = c(
      -val_max_diff_win_series_prop,
      +val_max_diff_win_series_prop
    ),
    midpoint = 0
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_val_o_series_win_prop_over_expected
save_for_slide(p_val_o_series_win_prop_over_expected)
```

@@

## Are offensive win %'s different in round 1?

@@

p_cod_o_win_r1_vs_post_round_prop <- cod_res_r1$plot +
  geom_curve(
    data = tibble(),
    aes(x = 1.2, y = 0.65, xend = 1.1, yend = 0.63),
    curvature = 0.2, 
    color = o_win_rx_prop_pal[["-1"]], 
    arrow = arw
  ) +
  geom_curve(
    data = tibble(),
    aes(x = 1.24, y = 0.27, xend = 1.1, yend = 0.27),
    curvature = 0-.2, 
    color = o_win_rx_prop_pal[["1"]], 
    arrow = arw
  ) +
  geom_text(
    data = tibble(
      x = c(1.2, 1.24),
      y = c(0.65, 0.27),
      hjust = c(0, 0),
      vjust = c(0.5, 0.5),
      lab = c(
        sprintf(
          'Largest negative percent difference in round 1\nvs. all other round win percentages (%+.0f%%).', 
          100 * cod_res_r1$largest_neg_diff_prop
        ),
        sprintf(
          'Largest positive percent difference (%+.0f%%).\nOnly significant difference (p value < 0.01).',
          100 * cod_res_r1$largest_pos_diff_prop
        )
      )
    ),
    color = 'white',
    size = 9 / .pt,
    aes(x = x, y = y, hjust = hjust, vjust = vjust, label = lab)
  )
p_cod_o_win_r1_vs_post_round_prop
save_for_slide(p_cod_o_win_r1_vs_post_round_prop)
```

@@

p_cod_series_outcome_prop_over_expected <- cod_long_series_outcome_prop |> 
  ggplot() +
  aes(x = record, y = outcome_idx) +
  geom_tile(
    data = cod_long_series_outcome_prop |> filter(outcome_idx > 1),
    show.legend = FALSE,
    # height = 0.8,
    aes(fill = value)
  ) +
  ggsci::scale_fill_material(
    palette = 'light-blue'
  ) +
  ggnewscale::new_scale_fill() +
  geom_tile(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1),
    show.legend = FALSE,
    height = 0.8,
    aes(fill = value)
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('purple'),
    high = extract_ggsci_mid_color('green'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_series_outcome_prop, 
      +cod_max_diff_series_outcome_prop
    )
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 3),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 2),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%.1f%%', 100 * value))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%+.1f%%', 100 * value))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
    color = 'white',
    size = 11 / .pt,
    aes(label = sprintf('%+.1f%%', 100 * value))
  ) +
  scale_x_discrete(
    position = 'top',
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    labels = c('Diff.', 'Expected', 'Actual'),
    breaks = 1:3,
    expand = c(0, 0)
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  labs(
    title = 'Series outcome %',
    x = NULL,
    y = NULL
  ) +
  common_cod_labs() 
p_cod_series_outcome_prop_over_expected
save_for_slide(p_cod_series_outcome_prop_over_expected)
```

@@

p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
  ggplot() +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 7, 
    .palette = 'pink', 
    .is_new = FALSE
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 8, 
    .palette = 'light-blue'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 9, 
    .palette = 'light-green'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 10, 
    .palette = 'amber'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 11, 
    .palette = 'deep-orange
  ') +
  b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
  scale_x_continuous(
    labels = 2:11,
    breaks = seq(2.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Back-to-back round win %',
    x = 'Round',
    y = '# of cod_rounds in Complete Series'
  ) + 
  geom_text(
    data = tibble(
      label = 'Back-to-back wins occur most\nfrequently in the last round.',
      x = 9.5,
      y = 8.5
    ),
    size = 9 / .pt,
    fontface = 'bold',
    color = 'white',
    hjust = 0,
    vjust = 0.5,
    aes(x = x, y = y, label = label)
  ) +
  map(
    cod_b2b_round_win_prop_arws |> group_split(rn), 
    function(.x) {
      geom_curve(
        data = data.frame(),
        color = 'white',
        arrow = arw,
        aes(x = .x$x, y = .x$y, xend = .x$xend, yend = .x$yend),
        curvature = .x$curvature
      )
    }
  )
p_cod_b2b_round_win_prop
save_for_slide(p_cod_b2b_round_win_prop)
# ## now accounting for number of cod_rounds that end up being played AND series winners...
# cod_rounds |> 
#   filter(win_series, n_rounds > 6L) |> 
#   summarize_b2b_round_wins(n_rounds)
# 
# ## and the losers...
# cod_rounds |> 
#   filter(!win_series) |> 
#   summarize_b2b_round_wins(n_rounds)
```

>>>>

```{r}
#| label: setup-eval
library(tidyverse)
library(extrafont)
library(ggtext)
library(ggsci)
library(ggnewscale)
library(magick)

blackish_background <- '#191919' ## to match slide background
gray_points <- '#4d4d4d'
gray_text <- '#999999'

font <- 'Titillium Web'
extrafont::loadfonts(quiet = TRUE)
theme_set(theme_minimal())
theme_update(
  text = element_text(family = font),
  title = element_text(size = 14, color = 'white'),
  plot.title = element_text(face = 'bold', size = 20, color = 'white'),
  plot.title.position = 'plot',
  plot.subtitle = element_text(size = 14, color = '#f1f1f1'),
  axis.text = element_text(color = 'white', size = 14),
  axis.title = element_text(size = 14, color = 'white', face = 'bold', hjust = 0.99),
  axis.line = element_blank(),
  panel.grid.major = element_line(color = gray_points),
  panel.grid.minor = element_line(color = gray_points),
  panel.grid.minor.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  strip.text = element_text(color = 'white', size = 16, face = 'bold'),
  plot.margin = margin(10, 10, 10, 10),
  plot.background = element_rect(fill = blackish_background, color = blackish_background),
  plot.caption = element_text(size = 12, color = 'white', hjust = 1),
  plot.caption.position = 'plot',
  plot.tag = ggtext::element_markdown(size = 12, color = 'white', hjust = 0),
  plot.tag.position = c(0.01, 0.01),
  panel.background = element_rect(fill = blackish_background, color = blackish_background)
)
update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
update_geom_defaults('point', list(color = 'white'))
update_geom_defaults('segment', list(color = 'white'))

add_logo <- function(
    path,
    path_logo,
    idx_x,
    idx_y,
    logo_scale = 0.1,
    adjust_x = TRUE,
    adjust_y = TRUE,
    path_suffix = '_w_logo',
    delete = TRUE
) {

  plot <- magick::image_read(path)
  logo_raw <- magick::image_read(path_logo)

  plot_height <- magick::image_info(plot)$height
  plot_width <- magick::image_info(plot)$width

  logo <- magick::image_scale(logo_raw, as.character(round(plot_width * logo_scale)))

  info <- magick::image_info(logo)
  logo_width <- info$width
  logo_height <- info$height

  x_pos <- plot_width - idx_x * plot_width
  y_pos <- plot_height - idx_y * plot_height

  if (adjust_x) {
    x_pos <- x_pos - logo_width
  }

  if (adjust_y) {
    y_pos <- y_pos - logo_height
  }

  offset <- paste0('+', x_pos, '+', y_pos)

  img <- magick::image_composite(plot, logo, offset = offset)
  ext <- tools::file_ext(path)
  rgx_ext <- sprintf('[.]%s$', ext)

  res <- magick::image_write(
    img,
    gsub(rgx_ext, sprintf('%s.%s', path_suffix, ext), path)
  )

  if (!delete) {
    return(res)
  }
  unlink(path, recursive = TRUE, force = TRUE)
  res
}

```

@@

## What are your chances of winning the next round ([COD SnD]{.cod})?

@@

.dpi <- 300
save_plot_for_slide <- function(
    p, 
    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
    width = 7.5, 
    height = width / 1.5,
    units = 'px',
    dpi = .dpi,
    # game = c('cod', 'val'),
    ...
) {

  path <- ggsave(
    plot = p,
    filename = filename,
    width = width * dpi,
    height = height * dpi,
    units = units,
    dpi = dpi,
    ...
  )
  is_cod <- filename |> str_detect('cod_')
  game <- ifelse(is_cod, 'cod', 'val')
  logo_scale <- ifelse(is_cod, 0.15, 0.07)
  add_logo(
    path,
    path_logo = file.path('images', sprintf('%s.png', game)),
    delete = FALSE,
    path_suffix = '',
    logo_scale = logo_scale,
    idx_x = 0.99,
    idx_y = 0.01,
    adjust_x = FALSE
  )
}

@@

p_cod_o_round_win_prop <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop,
    .f = o_round_win_text_layer,
    .threshold = 0.52,
    .labeller = cod_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_cod_o_round_win_prop
save_plot_for_slide(p_cod_o_round_win_prop)
```

@@

cod_max_diff_win_round_prop <- max(abs(cod_o_win_prop$diff_win_round_prop))
p_cod_o_round_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'diff_win_round_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_round_win_over_expected_text_layer,
    .threshold = -0.1,
    .labeller = cod_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('purple'),
    high = extract_ggsci_mid_color('green'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_round_prop, 
      +cod_max_diff_win_round_prop
    )
  ) +
  labs(
    title = 'Offensive Round Win % Over Expected'
  )
p_cod_o_round_win_prop_over_expected
save_plot_for_slide(p_cod_o_round_win_prop_over_expected)
```

@@

## What are your chances of winning the next round ([Valorant]{.valorant})?

@@

p_val_o_round_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  geom_path(
    data = val_pre_swap_round_segments,
    color = 'white',
    size = 1.5,
    aes(
      x = pre_cumu_w, 
      y = pre_cumu_l
    )
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_round_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_val_o_round_win_prop
save_plot_for_slide(p_val_o_round_win_prop)
```

@@

## What are your chances of winning the series ([COD SnD]{.cod})?

@@

p_cod_o_series_win_prop <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'win_series_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_series_win_text_layer,
    .threshold = 0.8,
    .labeller = cod_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('orange') +
  labs(
    title = 'Offensive Series Win %'
  )
p_cod_o_series_win_prop
save_plot_for_slide(p_cod_o_series_win_prop)
```

@@

cod_max_diff_win_series_prop <- max(abs(cod_o_win_prop$diff_win_series_prop))
p_cod_o_series_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.08,
    .labeller = cod_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_series_prop, 
      +cod_max_diff_win_series_prop
    )
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_cod_o_series_win_prop_over_expected
save_plot_for_slide(p_cod_o_series_win_prop_over_expected)
```

@@

## What are your chances of winning the series ([Valorant]{.valorant})?

```{r}
#| label: p_val_o_series_win_prop
p_val_o_series_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_series_prop') +
  geom_path(
    data = val_pre_swap_round_segments,
    color = 'white',
    size = 1.5,
    aes(
      x = pre_cumu_w, 
      y = pre_cumu_l
    )
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('orange') +
  labs(
    title = 'Offensive Series Win %'
  )
p_val_o_series_win_prop
save_plot_for_slide(p_val_o_series_win_prop)
```

@@

## What are your chances of winning the series ([Valorant]{.valorant})?

@@

val_max_diff_win_series_prop <- max(abs(val_o_win_prop$diff_win_series_prop))
p_val_o_series_win_prop_over_expected <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.2,
    .labeller = val_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    limits = c(
      -val_max_diff_win_series_prop,
      +val_max_diff_win_series_prop
    ),
    midpoint = 0
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_val_o_series_win_prop_over_expected
save_plot_for_slide(p_val_o_series_win_prop_over_expected)
```

@@

## Are offensive win %'s different in round 1 ([COD SnD]{.cod}?

@@

p_cod_o_win_r1_vs_post_round_prop <- cod_res_r1$plot +
  geom_curve(
    data = tibble(),
    aes(x = 1.2, y = 0.65, xend = 1.1, yend = 0.63),
    curvature = 0.2, 
    color = o_win_rx_prop_pal[["-1"]], 
    arrow = arw
  ) +
  geom_curve(
    data = tibble(),
    aes(x = 1.24, y = 0.27, xend = 1.1, yend = 0.27),
    curvature = 0-.2, 
    color = o_win_rx_prop_pal[["1"]], 
    arrow = arw
  ) +
  geom_text(
    data = tibble(
      x = c(1.2, 1.24),
      y = c(0.65, 0.27),
      hjust = c(0, 0),
      vjust = c(0.5, 0.5),
      lab = c(
        sprintf(
          'Largest negative percent difference in round 1\nvs. all other round win percentages (%+.0f%%).', 
          100 * cod_res_r1$largest_neg_diff_prop
        ),
        sprintf(
          'Largest positive percent difference (%+.0f%%).\nOnly significant difference (p value < 0.01).',
          100 * cod_res_r1$largest_pos_diff_prop
        )
      )
    ),
    color = 'white',
    size = 9 / .pt,
    aes(x = x, y = y, hjust = hjust, vjust = vjust, label = lab)
  )
p_cod_o_win_r1_vs_post_round_prop
save_plot_for_slide(p_cod_o_win_r1_vs_post_round_prop)
```

@@

p_cod_series_outcome_prop_over_expected <- cod_long_series_outcome_prop |> 
  ggplot() +
  aes(x = record, y = outcome_idx) +
  geom_tile(
    data = cod_long_series_outcome_prop |> filter(outcome_idx > 1),
    show.legend = FALSE,
    # height = 0.8,
    aes(fill = value)
  ) +
  ggsci::scale_fill_material(
    palette = 'light-blue'
  ) +
  ggnewscale::new_scale_fill() +
  geom_tile(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1),
    show.legend = FALSE,
    height = 0.8,
    aes(fill = value)
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('purple'),
    high = extract_ggsci_mid_color('green'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_series_outcome_prop, 
      +cod_max_diff_series_outcome_prop
    )
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 3),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 2),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%.1f%%', 100 * value))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
    color = blackish_background,
    size = 11 / .pt,
    aes(label = sprintf('%+.1f%%', 100 * value))
  ) +
  geom_text(
    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
    color = 'white',
    size = 11 / .pt,
    aes(label = sprintf('%+.1f%%', 100 * value))
  ) +
  scale_x_discrete(
    position = 'top',
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    labels = c('Diff.', 'Expected', 'Actual'),
    breaks = 1:3,
    expand = c(0, 0)
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  labs(
    title = 'Series outcome %',
    x = NULL,
    y = NULL
  ) +
  common_cod_labs() 
p_cod_series_outcome_prop_over_expected
save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
```

@@

p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
  ggplot() +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 7, 
    .palette = 'pink', 
    .is_new = FALSE
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 8, 
    .palette = 'light-blue'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 9, 
    .palette = 'light-green'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 10, 
    .palette = 'amber'
  ) +
  b2b_round_win_prop_tile_layer(
    .df = cod_b2b_round_win_prop, 
    .round = 11, 
    .palette = 'deep-orange
  ') +
  b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
  scale_x_continuous(
    labels = 2:11,
    breaks = seq(2.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  theme(
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Back-to-back round win %',
    x = 'Round',
    y = '# of cod_rounds in Complete Series'
  ) + 
  geom_text(
    data = tibble(
      label = 'Back-to-back wins occur most\nfrequently in the last round.',
      x = 9.5,
      y = 8.5
    ),
    size = 9 / .pt,
    fontface = 'bold',
    color = 'white',
    hjust = 0,
    vjust = 0.5,
    aes(x = x, y = y, label = label)
  ) +
  map(
    cod_b2b_round_win_prop_arws |> group_split(rn), 
    function(.x) {
      geom_curve(
        data = data.frame(),
        color = 'white',
        arrow = arw,
        aes(x = .x$x, y = .x$y, xend = .x$xend, yend = .x$yend),
        curvature = .x$curvature
      )
    }
  )
p_cod_b2b_round_win_prop
save_plot_for_slide(p_cod_b2b_round_win_prop)
# ## now accounting for number of cod_rounds that end up being played AND series winners...
# cod_rounds |> 
#   filter(win_series, n_rounds > 6L) |> 
#   summarize_b2b_round_wins(n_rounds)
# 
# ## and the losers...
# cod_rounds |> 
#   filter(!win_series) |> 
#   summarize_b2b_round_wins(n_rounds)
```
